Evaluation of performances

### 2021-06-21 analysis/eval-performance.Rmd

@@

Plot 1: Luiando
Plot 2: Laukiz2
Plot 3: Laukiz 1
Plot 4: Oiartzun

@@

Plot 1: Laukiz1
Plot 2: Oiartzun
Plot 3: Luiando
Plot 4: Laukiz2

@@

Plot 1: Luiando
Plot 2: Laukiz1
Plot 3: Oiartzun
Plot 4: Laukiz2

@@

                                 TRUE ~ as.character(iter))) %>% 
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::mutate(fw.perc = fw.perc * 100) %>%
  dplyr::rename("Features (\\%)" = fw.perc) %>%
  dplyr::mutate(`Test Plot` = as.character(Plot)) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF \\\\ Relief" = "RF MBO Relief", "XGB \\\\ CMIM" = "XGBOOST MBO CMIM",
    "SVM \\\\ Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(`Test Plot` = as.character(`Test Plot`)) %>%
  dplyr::mutate("\\#" = case_when(
    `Test Plot` == "Laukiz1" ~ ceiling((`Features (\\%)` * 559) / 100),
    `Test Plot` == "Laukiz2" ~ ceiling((`Features (\\%)` * 451) / 100),
    `Test Plot` == "Luiando" ~ ceiling((`Features (\\%)` * 301) / 100),
    `Test Plot` == "Oiartzun" ~ ceiling((`Features (\\%)` * 497) / 100),
  )) %>%
  dplyr::group_by(Learner) %>%
  dplyr::select(Learner, `Test Plot`, "Features (\\%)", "\\#", RMSE)

@@

table4 <- df_tbl %>%
  xtable::xtable(
    type = "latex",
    caption = "Selected feature portions during tuning for the best performing learner-filter settings (SVM Relief, RF Relief, XGBoost CMIM) across folds for task HR-NRI-VI, sorted by plot name. \texttt{#} denotes the absolute number of features selected and 'Features (\texttt{%})' refers to the percentage relative to the overall features available (7675). Results were estimated in a separate model tuning step, not within the main cross-validation comparison.",
    label = "tab:tune-perc-sel-features",
    digits = c(0, 0, 0, 5, 0, 2)
  )

>>>>

Example for RF on fold 1 (Luiando):

- Percentage of selected features during tuning on all plots but Luiando: `bmr_inspect_tune[["results"]][["hr_nri_vi"]][["RF MBO Relief"]][["extract"]][[1]][["mbo.result"]][["x"]][["fw.perc"]]`: 99.972
- Overall features available in training set: sum(Laukiz1 + Laukiz2 + Oiartzun) = 1507
- Absolute number of selected features: 1507 * 0.99972 = 1507

@@

- Plot 1: Luiando
- Plot 2: Laukiz2
- Plot 3: Laukiz 1
- Plot 4: Oiartzun

@@

- Plot 1: Laukiz1
- Plot 2: Oiartzun
- Plot 3: Luiando
- Plot 4: Laukiz2

@@

- Plot 1: Luiando
- Plot 2: Laukiz1
- Plot 3: Oiartzun
- Plot 4: Laukiz2

@@

                                 TRUE ~ as.character(iter))) %>% 
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::mutate(fw.perc = fw.perc * 100) %>%
  dplyr::rename("Features (\\%)" = fw.perc) %>%
  dplyr::mutate(`Test Plot` = as.character(Plot)) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF \\\\ Relief" = "RF MBO Relief", "XGB \\\\ CMIM" = "XGBOOST MBO CMIM",
    "SVM \\\\ Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(`Test Plot` = as.character(`Test Plot`)) %>%
  dplyr::mutate("\\#" = case_when(
    # numbers here are the respective sums of the training sets (without the mentioned plot acting as the test set)
    `Test Plot` == "Laukiz1" ~ paste0(as.character(ceiling((`Features (\\%)` * 1249) / 100)), "/1249"),
    `Test Plot` == "Laukiz2" ~ paste0(as.character(ceiling((`Features (\\%)` * 1357) / 100)),"/1357"),
    `Test Plot` == "Luiando" ~ paste0(as.character(ceiling((`Features (\\%)` * 1507) / 100)),"/1507"),
    `Test Plot` == "Oiartzun" ~ paste0(as.character(ceiling((`Features (\\%)` * 1311) / 100)),"/1311"),
  )) %>%
  dplyr::group_by(Learner) %>%
  dplyr::arrange(Learner, `Test Plot`) %>% 
  dplyr::select(Learner, `Test Plot`, "Features (\\%)", "\\#", RMSE)

@@

table4 <- df_tbl %>%
  xtable::xtable(
    type = "latex",
    caption = "Selected feature portions during tuning for the best performing learner-filter settings (SVM Relief, RF Relief, XGBoost CMIM) across folds for task HR-NRI-VI, sorted by plot name. \\texttt{#} denotes the absolute number of features selected and 'Features (\\texttt{%})' refers to the percentage relative to the overall features available in the training sets for each plot (Laukiz1 = 1249, Laukiz2 = 1357, Luiando = 1507, Oiartzun = 1311). Results were estimated in a separate model tuning step, not within the main cross-validation comparison.",
    label = "tab:tune-perc-sel-features",
    digits = c(0, 0, 0, 5, 0, 2)
  )
